\documentclass[line, margin]{res}
\begin{document}
\name{Behnam JabbariZadeh}
\address{London, Ontario \\ 226-577-3101 \\ bjabbar@uwo.ca \\ linkedin.com/in/behnam-jabbarizadeh }

\begin{resume}
  \section{SUMMARY}
  Bioinformatics researcher with experience in analyzing Next-Generation sequencing data (single cell RNA seq) and a strong background in computer science.
  Developed a novel method for batch effect analysis that outperformed other methods.
  Skilled in R and Python programming, Linux HPC environments, and cloud computing platforms.
  Seeking opportunities to apply technical skills and contribute to innovative projects.
  \section{EXPERIENCE}
  {\sl Bioinformatics researcher} \hfill September 2021 - Present \\
  London Health Sciences Centre Victoria Hospital, London, Ontario.\\
  \begin{itemize} \itemsep -2pt
    \item Developed a \textbf{novel} method for batch effect analysis in \textbf{single cell RNA seq data} that outperforms other methods, improving data quality and reducing batch effects in downstream analyses.
    \item Integrated multiple research projects from different databases, facilitating cross-project analyses and enabling new discoveries.
    \item Utilized Compute Canada resources to run analyses on a \textbf{Linux HPC environment}, writing scripts in \textbf{R} and Linux.
  \end{itemize}
  {\sl Teaching assistant} \hfill September 2021 - May 2022 \\
  Western University, London, Ontario
  \begin{itemize} \itemsep -2pt
    \item Mentored over 100 students for two university terms, delivering lectures and providing guidance on \textbf{Python} programming language.
    \item Assisted students with \textbf{debugging} code and implementing their ideas for class projects.
  \end{itemize}
  \section{SKILLS}
  \begin{itemize} \itemsep -2pt
  \item Programming Languages: Python, R, C++
  \item Software Tools: JIRA, Git, Docker
  \item Operating Systems: Linux, macOS, Windows
  \item Experience with HPC environments and cloud computing platforms
  \end{itemize}

\section{EDUCATION}
{\sl MSc}, Computer Science, Bioinformatics \hfill September 2021 - March 2023\\
Western University, London, Canada \\
Relevant Coursework: Bioinformatics, Computational Biology, Algorithms and Data Structures
\\ \\
{\sl BSc}, Electrical engineering \hfill September 2015 - October 2020\\
Amirkabir University, Tehran, Iran 
\section{CERTIFICATES}
Introduction to genomic technologies, Coursera, John Hopkins University
\section{VOLUNTEER EXPERIECE}
Assistant manager \hfill August 2019 - September 2021 \\
Innovation Center of Amirkabir university of technology, Tehran, Iran 
\begin{itemize}\itemsep -2pt
\item Mentored students through the creation and growth of their projects.
\item Utilized the project management software \textbf{JIRA} to efficiently organize and oversee team operations 
\item Organized more than 10 educational workshops and helped over 20 student teams gain acceptance into our program.
\end{itemize}
\end{resume}
\end{document}